\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

This `Unofficial How-To Guide' provides step-by-step instructions for a range of tasks, including making cables, unjamming fans, replacing power supplies, and so on. It draws on the personal experience of the authors and the combined skills and knowledge of users of the NABU forum.\footnotemark  The tasks described range from simple \mbox{(\difficulty{1})}, requiring few skills or tools, to fiendish \mbox{(\difficulty{5})}, requiring considerable experience or specialist tools.

\vskip.25em
This guide is `unofficial` because by the time of its creation, the NABU Manufacturing Corp. had been out of business for almost 40 years and so was in no position to sanction its publication. It is also `unofficial' because no one person, or even a group of people, can claim to speak for the NABU community. In many respects, this guide is a joint effort, based on the contributions from numerous people. And while the instructions in this guide are believed to be correct, they are in no way official or even the only way to achieve the stated objectives. Which leads into the final reason for this guide being `unofficial'. If through following any of the instructions in this guide you damage your NABU system or anything else, or hurt yourself or others, you will have no one to blame but yourself. Like many things in life, this guide comes with no guarantees, implied or otherwise. That said -- and while there are \textit{definitely absolutely no guarantees!} -- if you \textit{do} run into problems, you \textit{may} find solace and potentially even solutions in the NABU forum.

\vskip.25em
Finally, if you would like to provide feedback on this guide, either because you've spotted an error of some kind, or because you have one or more suggestions, or for any other reason, please raise a Github `issue' at \mbox{<https://github.com/dimitrit/nabu-howto/issues>}.
\footnotetext{The NABU forum is hosted by the RetroNet team at <https://forums.nabu.ca>.}

\vskip2.5em
\null\hspace{.66\linewidth} DT, April 2023

